Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-05-23 inc/design_considerations/considerations.tex
tweak into to considerations chapter

In Chapters \ref{chap:ms_model} through \ref{chap:model_results}, I have explored the mathematical side of designing an ultrafast electron microscope; modeling the behavior of a pulse and the effects that column elements have upon it.
However, since microscopy is an experimental science, we are also designing and building a prototype UEM system at UIC.
In doing so we have decided that special care must be given to the creation and propagation of the electron beam.
In the case of single-shot UEM, in which the image of the sample is acquired using only one electron pulse, several factors lead to two major considerations: first, that a large area photoemission source is required to smaller area or even single point emitters, and second, that the ``normalized transverse emittance,'' a beam quality figure of merit which will be defined later, must be minimized.

>>>>

In Chapters \ref{chap:ms_model} through \ref{chap:model_results}, I have explored the mathematical side of designing an ultrafast electron microscope; modeling the behavior of a pulse and the effects that column elements have upon it.
However, since microscopy is an experimental science, we are also designing and building a prototype UEM system at UIC.
In doing so we have decided that special care must be given to the creation and propagation of the electron beam.
In the case of single-shot UEM, in which the image of the sample is acquired using only one electron pulse, several factors lead to two major considerations: first, that a large area photoemission source is required versus smaller area or even single point emitters, and second, that the ``normalized transverse emittance,'' a beam quality figure of merit which will be defined later, must be minimized.
